
We look to determine a metric (or distance) between the years of the corpus that can show a linguistic drift. Intuitively, the language nowadays and 10 years ago is relatively the same, but there is more differences with the language of 200 years ago. It should be a smooth evolution and we want to find a way to characterize it mathematically. Here are some properties that we defined for a distance $d$ between two subsets of the corpus $C_i$ and $C_{i'}$:

\begin{itemize}
 \item Normalization: $0 \leq d(C_i,C_{i'}) \leq 1$.
 \item Distance between a subset and itself is zero: $C_i = C_{i'} \Rightarrow d(C_i,C_{i'}) = 0$.
 \item The distance should be almost similar for consecutive years while increasing as years become distant.
 \item The distance should not depend on the size of the corpus.
\end{itemize}

In the following, distances will be represented in matrices of size $N \times N$, with $N = 159$ years corresponding to the interval of years building our corpus:
\[
\begin{matrix}
 & year1 & year2 & ... & yearN \\
 year1 & \mathbf{0} & \mathbf{d(year1,year2)} & ... & \mathbf{d(year1,yearN)} \\
 year2 & \mathbf{d(year2,year1)} & \mathbf{0} & ... & \mathbf{d(year2,yearN)} \\
 ... & ... & ... & ... & ... \\
 yearN & \mathbf{d(yearN,year1)} & \mathbf{d(yearN,year2)} & ... & \mathbf{0}
\end{matrix}
\]
We tried several metrics that are presented in the next subsections. We also put a set of criteria that we could use to judge that a metric is better than another one.\\
For the robustness, the size of the corpus shouldn't influence the distance. Thus, the distance between a subset of a set $C_i$ and a subset of another set $C_{i'}$ should be the same as the distance between the whole sets $C_i$ and $C_{i'}$.\\
Secondly, the distance should be robust considering OCR unresolved errors.\\
We also proceeded a datation of articles for each metric to compare the efficiency of each one. We would estimate that a datation is efficient if, when computing the distance of an article with each year or years intervals, then the smaller distance should assign the text to a year with 10 years margin.\\
Finally, in the matrix plot, the colour should fade out homogeneously from the diagonal to the opposite corners. There should be a kind of 'band' around the diagonal.
