\section{OCR Correction}
\subsection{Why do we need to clean the OCR?}

Limited by the optical character recognition, OCR documents comprise of a significant amount of erroneous words. Since our project rely heavily on word matching between documents, we need to deal with OCR error before we apply advance similarity calculation methods. 

Moreover, with all that said, the practical reality is that many OCR errors are quite predictable. So it is possible, and useful, to produce a pretty-good list of rules that simply translates individual tokens back into correctly spelled words. In this part, we utilized one simplest approach, i.e. to develop a set of rules to translate individual tokens produced by OCR errors back into correctly-spelled forms.

In order to found the impact of OCR correction, in the later section \ref{metrics} about metrics, we also experimented different metrics on OCR corrected dataset and OCR non-corrected dataset to find out whether OCR will play a significant effect upon the accuracy of metrics.

\subsection{Clean Strategy}
Since we need to pay more attention to the linguistic shift, here, for the OCR correction, we chose simplest approach and identified a set of predictable character substitutions. 

\begin{enumerate}[1.]
\item Basic Replacement Rule

We apply some common replacement rules to make the OCR word to be the same form.
	\begin{enumerate}[1.]
	\item Remove capital letter
	\item Remove alone letter
	\item Remove punctuation
	\item Remove accent
	\item Remove special letter (e.g., ;, /, -, ', \&)
	\end{enumerate}
\item Apply a set of predictable character substitutions

	In this part, we identified a set of common OCR error and do basic word replacement.

		\begin{enumerate}[1.]
		\item Replace complete word

		We replaced complete word if current n-grams exists a match with the word that in the dictionary, e.g., $so \rightarrow se$, $pir \rightarrow par$, $pavs \rightarrow pays$.

		\item Replace part of word

		For the matching of the partial word, we also use regular expression to find the corresponding word and its replacement word, e.g., $iii \rightarrow m$, $ii \rightarrow n$, $q.([a-z]) \rightarrow qu?$. Actually, most of wrong OCR words are local errors, and the substitution of local error plays a significant role in the OCR correction. 

		\end{enumerate}

\end{enumerate}