\clearpage
\begin{thebibliography}{20}
\bibitem{} Vincent Buntinx, Human Language Technology: A study of linguistic drift on a corpus of 4 000 000 of digitized newspaper, DHLAB / CDH / EPFL
\bibitem{} M. Rajman and L. Lebart. Similarités pour données textuelles. Proc. of 4th International Conference on Statistical Analysis of Textual Data (JADT'98), pp. 545-555, Nice (France), 1998
\bibitem{} R. Besançon, M. Rajman and J.-C. Chappelier. Textual Similarities based on a Distributional Approach. Proceedings of the Tenth International Workshop on Database and Expert Systems Applications (DEXA99), pp. 180-184, Firenze (Italy), 1999
\bibitem{} R. Besançon and M. Rajman. Evaluation of a Vector Space similarity measure in a multilingual framework. Proceedings of the Third International Conference on Language Resource and Evaluation (LREC'2002), May, 2002
\bibitem{} St-Jacques and C. Barrière. Similarity judgments: philosophical, psychological and mathematical investigations. In Proceedings of the Workshop on Linguistic Distances (LD '06). Association for Computational Linguistics, Stroudsburg, PA, USA, 8-15, 2006
\bibitem{} J.-B. Michel et al. Quantitative Analysis of Culture Using Millions of Digitized Books. Science 331, 17, 2011. DOI: 10.1126/science.1199644
\bibitem{} F. Kaplan. Linguistic Capitalism and Algorithmic Mediation. In Representations, vol. 127, num. 1, p. 57-63, 2014
\bibitem{} V. Niculae, M. Zampieri, L. P. Dinu and A. M. Ciobanu. Temporal Text Ranking and Automatic Dating of Texts. Proceedings of the 14th Conference of the European Chapter of the Association for Computational Linguistics (EACL), Gothenburg (Sweden), 2014
\bibitem{} Zampieri, Marcos. Using bag-of-words to distinguish similar languages: How efficient are they?. In : Computational Intelligence and Informatics (CINTI), 2013 IEEE 14th International Symposium on. IEEE, 2013. p. 37-41.
\bibitem{} C Buckley, G. Salton. Term weigthing Approaches in automatic Text retrieval. Information Processing and management, 24:513-523, 1988
\end{thebibliography} 